Forecasting the 2024 US Presidential Election: A Poll-Based Approach

### 2024-10-31 paper/paper.qmd

@@

# View the final results
print(final_results)

@@

@@

# View the results with differences
print(intercept_wide)
```

>>>>

  if (nrow(candidate_data) > 0) {  # Check if there are rows for the candidate
    model <- lm(pct ~ days_towards_election, data = candidate_data)
    tidy_model <- tidy(model)  # Get a tidy summary of the model
    tidy_model$candidate <- candidate  # Add candidate to the output
    return(tidy_model)
  } else {
    return(NULL)  # Return NULL if no data for the candidate
  }
}

@@

# View the final results
kable(final_results)

@@

fit_model <- function(data, candidate) {
  candidate_data <- data %>% filter(candidate_name == candidate)

@@

# View the results with differences
kable(intercept_wide)
```
